Introduction to Causal Inference Models

### 2017-07-12 msm_introduction.Rmd
updated slidy presentation.

- Two general categories that have been around for a decade or so

1. Structural nested models 
- Commonly referred to as g-estimation, g-computation, g-formula, g-something
- The g stands for "general"

2. Marginal structural models 
- Sometimes called inverse-probability-of-treatment weighting (IPTW)

- Newer approach in recent years are the doubly-robust method which we will touch on later

@@

We get pretty much the same result using the g-formula approach to a standard regression.

## Counterfactual Estimate using IPTW

>>>>

- Two general categories of commonly used causal inference methods

1. Parametric g-formula (sometimes called simple substitution)

2. Marginal structural models (Inverse-probability-of-treatment weighting [IPTW])

@@

We get pretty much the same result using the g-formula approach to a standard regression. However, we've now made our "what if?" question explicit and testable.

## Counterfactual Estimate using IPTW
Another commonly use method is the inverse-probability-of-treatment weight.
